---
title: "Grad School Survey"
author: "Roger Tu"
date: "September 3, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import and initialize the graduate student survey data.

```{r, include = FALSE, echo=FALSE}
library(ggplot2)
library(reshape2)
library(dplyr)
df <- read.csv("c:/Users/turog/Downloads/Grad_Student_Survey_2019.csv", header = TRUE)
dimensions <- names(df)
```

Index graduate student dataframe columns.

```{r, , echo=FALSE}
general <- dimensions[2:11]
lounge <- dimensions[12:15]
admission <- dimensions[16:36]
retreat <- dimensions[37:44]
bicos_sat <- dimensions[46:53]
prog_sat <- dimensions[55:73]
mileston <- dimensions[75:78]
resource <- dimensions[79]
policies <- dimensions[80:91]
skills_A <- dimensions[93:98]
skills_B <- dimensions[99:104]
training <- dimensions[105:129]
committ <- dimensions[131:150]
advisor <- dimensions[152:172]
co_advi <- dimensions[174:202]
finance <- dimensions[204:231]
mental <- dimensions[233:263]
stu_life <-dimensions[264:295]
harrass <- dimensions[296:328]
dev <- dimensions[329:341]
gsc <- dimensions[342:353]
extra <- dimensions[c(45,54,74,92,130,151,173,232)]
```

Create a vector containing all indices to be removed.

```{r, echo=FALSE}
to_Remove <- c()
to_Remove <- c(to_Remove, "Timestamp",
               bicos_sat,
               mileston, resource,
               policies,
               skills_A,skills_B,
               training,
               committ,advisor,co_advi,
               finance,mental,stu_life,harrass,dev,
               gsc, extra)
```

## Create the subsetted dataframe by removing all indices in dimensions from to_Remove

Fixed an index because someone wrote "24 I think" for a parameter that should have been numeric (This guy changed everything to a factor!!)

```{r, echo=FALSE}
df_names <- setdiff(dimensions, to_Remove)
df_roger <- df[df_names]

df_roger$How.old.are.you.[82]<- 24
```

## Created a theme for plotting.

x-axis text horizontally adjusted by +0.5. Axis is black. White background, border, major and minor lines.

```{r, echo=FALSE}
a_theme <- 'theme(axis.text.x = element_text(angle = 0, hjust = 0.5),
                 axis.line = element_line(colour = "black"),
                 panel.grid.major = element_blank(),
                 panel.grid.minor = element_blank(),
                 panel.border = element_blank(),
                 panel.background = element_blank())'
```

## Age of Graduate Students

```{r, echo = FALSE}
ggplot(data = df_roger) +
  geom_bar(aes(x = How.old.are.you.)) +
  labs(title = "Student Age", x = "Age", y = "Count") +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_discrete(expand = c(0,0)) +
  eval(parse(text=as.character(a_theme)))
```

## Of those who answered the survey: Age of Graduate Students by Year in Graduate School

```{r, echo = FALSE}
ggplot(data = df_roger, aes(x = What.year.are.you., y = as.numeric(as.character(How.old.are.you.)))) +
  geom_violin(fill = "gray") + geom_boxplot(width=0.1) +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = .2) +
  labs(title = "Student Age by Year in Grad School", x = "Year", y = "Age") +
  scale_y_continuous(breaks=seq(20,36,2)) +
  theme(legend.position = "none") +
  eval(parse(text=as.character(a_theme)))
```

## Graduate Student Survey Response by Year

```{r, echo = FALSE}
ggplot(data = df_roger, aes(x = What.year.are.you.)) +
  geom_bar() +
  labs(title = "Responses to Survey by Year in Grad School", x = "Year", y = "Number") +
  scale_y_continuous(expand = c(0,0), limits = c(0,36), breaks=seq(0,36,4)) +
  eval(parse(text=as.character(a_theme)))
```

## Graduate Student Survey Response by Gender

```{r, echo = FALSE}
ggplot(data = df_roger, aes(x = df_roger$What.is.your.gender.identity...check.all.that.apply.)) +
  geom_bar() + geom_text(stat = "count", aes(label = ..count..), vjust = -1) +
  labs(title = "Responses to Survey by Gender", x = "Gender", y = "Number") +
  scale_y_continuous(expand = c(0,0), limits = c(0,70), breaks=seq(0,70,10)) +
  eval(parse(text=as.character(a_theme))) + theme(axis.text.x = element_text(angle = 0, hjust = .5))
```

## Graduate Student Survey Response by Gender and Year

```{r, echo = FALSE}
ggplot(data = df_roger, aes(x = df_roger$What.year.are.you., fill = df_roger$What.is.your.gender.identity...check.all.that.apply.)) +
  geom_bar(color = "black", position=position_dodge()) +
  geom_text(stat = "count", aes(label = ..count..), position=position_dodge(1), vjust = -0.5, size = 3.5) +
  labs(title = "Gender Distribution by Year", x = "Year", y = "Number") + scale_fill_brewer(name = "Gender" , palette = "Greys") +
  scale_y_continuous(expand = c(0,0), limits = c(0,20), breaks=seq(0,20,2)) +
  eval(parse(text=as.character(a_theme))) +
  theme(legend.position = c(0.9,0.9))
```

## Response by Department

Most people only listed one department. Some listed Molecular Medicine + "xyz Department". For those who had more than one, they were categorized as Molecular Medicine

```{r,echo = FALSE}
df_roger$What.department.s..are.you.in.<- sub("^.*?(Molecular Medicine,).*|.*(, Molecular Medicine).*$", # Use RegEx to match _Molecular Medicine, or Molecular Medicine_
                                              "Molecular Medicine", # Replace the match with Molecular Medicine
                                              df_roger$What.department.s..are.you.in.)

ggplot(data = df_roger, aes(x = reorder(What.department.s..are.you.in., What.department.s..are.you.in., function(x)+length(x)), fill= In.which.campus.are.you.enrolled.)) + # gives reordering by count.
  geom_bar(color = "black", stat = "count", position= position_dodge()) +
  geom_text(stat = "count", aes(label = ..count..), position = position_dodge(1), vjust = -0.3, color = "black") +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) + # Method of "wrapping x-axis text"
  labs(title = "Student Survey Responses Home Department", x = "", y ="") +
  scale_fill_brewer(name = "" , palette = "Greys") +
  scale_y_continuous(expand = c(0,0), limits = c(0,40), breaks = seq(0,40,5)) +
  theme(legend.position = c(0.15,0.9)) +
  eval(parse(text=as.character(a_theme)))
```

## Response by Home Department and Lab Size

```{r, echo = FALSE}
# Order your factor by level.
df_roger$How.many.people.are.in.your.lab...including.students..postdocs..staff..admin.. <- factor(x = df_roger$How.many.people.are.in.your.lab...including.students..postdocs..staff..admin.., levels = c("1-5","6-10","11-15","16-20","21+"))

ggplot(data = df_roger, aes(x = What.department.s..are.you.in., fill = How.many.people.are.in.your.lab...including.students..postdocs..staff..admin..)) +
  geom_bar(color = "black", position = position_dodge()) +
  geom_text(stat = "count", aes(label = ..count..), position=position_dodge(1), vjust = -0.5, size = 3.5) +
  labs(title = "Department Size by Lab Size", x = "", y = "Number") + 
  scale_fill_brewer(name = "Total Lab Members", palette ="Greys") +
  scale_y_continuous(expand = c(0,0), limits = c(0,24), breaks = seq(0,24,2)) +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 10, simplify = FALSE), paste, collapse="\n")) + # Method of "wrapping x-axis text"
  eval(parse(text=as.character(a_theme))) +
  theme(axis.text.x = element_text(angle = 0, hjust = .5), legend.position = c(0.9, 0.85))
```

## Response by Lab Size

```{r, echo = FALSE}

ggplot(data = df_roger,aes(x = How.many.people.are.in.your.lab...including.students..postdocs..staff..admin..)) +
  geom_bar(color = "black") + geom_text(stat = "count", aes(label=..count..), vjust = 1.3, color = "white") +
  labs(title = "Number of Members in a Lab", x = "", y = "Number") + 
  scale_y_continuous(expand = c(0,0), limits = c(0,30), breaks=seq(0,30,5)) +
  eval(parse(text=as.character(a_theme)))
```

## Grad Students in Labs by Campus

```{r, echo = FALSE}
df_roger$How.many.graduate.students..including.yourself..are.in.your.lab. <- factor(df_roger$How.many.graduate.students..including.yourself..are.in.your.lab.,
                                                                                    levels = c("1", "2-5", "6-10", "11+"))

ggplot(data = df_roger, aes(x = How.many.graduate.students..including.yourself..are.in.your.lab., fill = In.which.campus.are.you.enrolled.)) +
  geom_bar(color = "black", position = position_dodge()) +
  geom_text(stat = "count", position = position_dodge(1), aes(label = ..count..), vjust = 1.3, color = "black") +
  labs(title = "Graduate Students in your lab by Campus", x = "Graduate Students in your lab (inclusive)", y = "Number") +
  scale_y_continuous(expand = c(0,0), limits = c(0,40), breaks = seq(0,40,5)) +
  scale_fill_brewer(name = "", palette = "Greys") +
  eval(parse(text=as.character(a_theme)))
```

## Campus

```{r, echo = FALSE}
ggplot(data = df_roger, aes(x = In.which.campus.are.you.enrolled.)) +
  geom_bar(color = "black", position = position_dodge()) +
  geom_text(stat = "count", position = position_dodge(1), aes(label = ..count..), vjust = 1.3, color = "white") +
  labs(title = "Distribution of Students who answered the survey", x = "", y = "") +
  scale_y_continuous(expand = c(0,0), limits = c(0,100), breaks=seq(0,100,10)) +
  eval(parse(text=as.character(a_theme)))
```

## Where to put the lounge
Had to Subset the data first and fill in the blanks.

```{r, echo = FALSE}
lounge_df<-df_roger[11:12] #subset
lounge_df$row_Name <- seq(1, length(lounge_df$I.would.utilize.a.graduate.student.lounge.located.on.the._____...1st.floor.of.Beckman.)) # add id #s
#Fill in the blanks
lounge_df$I.would.utilize.a.graduate.student.lounge.located.on.the._____...1st.floor.of.Beckman.<- sub("^$", "No Response", lounge_df$I.would.utilize.a.graduate.student.lounge.located.on.the._____...1st.floor.of.Beckman.)
lounge_df$I.would.utilize.a.graduate.student.lounge.located.on.the._____...3rd.floor.of.Hazen. <- sub("^$", "No Response", lounge_df$I.would.utilize.a.graduate.student.lounge.located.on.the._____...3rd.floor.of.Hazen.)
lounge_df2 <-melt(lounge_df, id = "row_Name") #reshape the df

#reorder the factors
lounge_df2$value <- factor(lounge_df2$value, levels = c("No Response", "Strongly disagree", "Disagree", "Neither agree nor disagree", "Agree", "Strongly agree"))

ggplot(data = lounge_df2 %>% filter(value != "No Response"), aes(x = value, fill = variable)) + #ctrl + shft + m gives you pipe. filter on value, need dplyr
  geom_bar(color = "black", position = position_dodge()) + 
  geom_text(stat = "count", position = position_dodge(1), aes(label = ..count..), vjust= 1.3, color = "black") +
  labs(title = "Graduate Lounge Location", x = "", y = "Number") +
  scale_fill_brewer(name = "Lounge in..", palette ="Greys", labels = c("Beckman", "Hazen")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,30), breaks=seq(0,30,5)) +
  eval(parse(text=as.character(a_theme))) + theme(legend.position = c(0.9,0.9))
```

## What was your experience prior to Scripps?

```{r, echo = FALSE}
ggplot(data = df_roger, aes(x = My.job.schooling.preceding.my.start.in.grad.school.at.TSRI.is.best.described.as.____., fill = What.year.are.you.)) + 
  geom_bar(color = "black", position = position_dodge()) +
  labs(title = "What were you doing preceding Graduate School", x = "", y = "") +
  geom_text(stat = "count", aes(label = ..count..), position = position_dodge(1), vjust = 1.3, size = 3.5) +
  scale_x_discrete(labels = c("Worked:\nAcademic Lab", "Worked: Industry \n (Science)", "Worked: Industry \n (Non-Science)", "School:\nBachelors", "School:\nMasters")) +
  scale_y_continuous(expand = c(0,0), limits = c(0,20), breaks = seq(0,20,2))+
  scale_fill_brewer(name = "Year", palette = "Greys") +
  eval(parse(text = as.character(a_theme))) +
  theme(legend.position = c(0.15, .9), legend.direction = "horizontal")
```

## Prentation, Publications and On-Campus Interviews

```{r, echo=FALSE}
prep_Prior_GS <- cbind(df_roger$What.year.are.you., df_roger[17:19])                # subset df
prep_Prior_GS_melt <- melt(prep_Prior_GS, id = c("df_roger$What.year.are.you."))    # melt df
prep_Prior_GS_melt$variable2 <- gsub("[.]", " ", prep_Prior_GS_melt$variable)       # replace all "." with " "
prep_Prior_GS_melt$variable2 <- gsub("before starting in the grad program", " ", prep_Prior_GS_melt$variable2) # replace that phrase with nothing
prep_Prior_GS_melt$value <- factor(prep_Prior_GS_melt$value, levels = c("Yes", "No"))     # Orders the Factor

ggplot(data = prep_Prior_GS_melt, aes(x = variable2, fill = value)) +
  geom_bar(color = "black", position = position_dodge()) +
  geom_text(stat = "count", aes(label = ..count..), position = position_dodge(1), vjust = 1, hjust = 1.5, size = 3.5) +
  labs(title = "Before starting in the grad program...", x = "", y = "") +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 17, simplify = FALSE), paste, collapse="\n")) + # Method of "wrapping x-axis text"
  scale_y_continuous(expand = c(0,0), limits = c(0,100), breaks = seq(0,100,20)) +
  scale_fill_brewer(name = "", palette ="Greys", labels = c("Yes", "No")) +
  coord_flip() +
  eval(parse(text = as.character(a_theme))) +
  theme(legend.position = c(0.9,0.9))
```

## Grad lounge recommendation

I'm gong to try and do a word cloud.  Here I'm transforming the data to remove weird funky stuff

```{r, include = FALSE, echo=FALSE}
library(tm)
library(SnowballC)
library(wordcloud)
df_roger$Please.provide.recommendations.for.the.graduate.student.lounge. <- sub("^$", "No Response", df_roger$Please.provide.recommendations.for.the.graduate.student.lounge.)

docs <- VCorpus(VectorSource(df_roger$Please.provide.recommendations.for.the.graduate.student.lounge.))

```
Text cleaning
```{r, echo=FALSE}
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, removeWords, c("no response", "response", "no","can","etc", "take", "reason","use", "maybe", "like", "seen","quite","used","separate","student","butler","usually","spot","away","long"))
docs <- tm_map(docs, stripWhitespace)
docs <- tm_map(docs, removePunctuation)
docsCopy <- docs
docs <- tm_map(docs, stemDocument)
```
Transformation of data to a matrix then to dataframe. Create a vector (docs2) and complete the stemmed words.
```{r, echo=FALSE}
dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m), decreasing = TRUE)
d <- data.frame(word = names(v), freq = v)

docs2 <- stemCompletion(d$word, dictionary = docsCopy, type = "shortest")
```
Build Word Cloud with stemmed words as input word, and frequency.
```{r, echo=FALSE}
set.seed(1234)
wordcloud(words = docs2, freq = d$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```

## Influences on Enrollment. 

Clean up the data... If entry has more than one, Changed entry to that lower level. Lots of clean up here.

```{r, echo=FALSE}
inf_Enroll <- cbind(df_roger$What.year.are.you., df_roger[20:28])                # subset df
inf_Enroll$How.did.the.following.factors.contribute.to.your.decision.in.choosing.Scripps.Research.for.graduate.school...Alumni.publications.or.other.success.outcomes.[41] <-  "Modestly contributed"
inf_Enroll$How.did.the.following.factors.contribute.to.your.decision.in.choosing.Scripps.Research.for.graduate.school...Alumni.publications.or.other.success.outcomes.[63] <- "Slightly contributed"
inf_Enroll$How.did.the.following.factors.contribute.to.your.decision.in.choosing.Scripps.Research.for.graduate.school...Alumni.publications.or.other.success.outcomes.[79] <- "Slightly contributed"
inf_Enroll$How.did.the.following.factors.contribute.to.your.decision.in.choosing.Scripps.Research.for.graduate.school...Alumni.publications.or.other.success.outcomes.[114] <- "Did not contribute"
inf_Enroll$How.did.the.following.factors.contribute.to.your.decision.in.choosing.Scripps.Research.for.graduate.school...External.factors.such.as.spouse.or.family.considerations.[26] <- "Did not contribute"
inf_Enroll$How.did.the.following.factors.contribute.to.your.decision.in.choosing.Scripps.Research.for.graduate.school...External.factors.such.as.spouse.or.family.considerations.[79] <- "Did not contribute"
inf_Enroll$How.did.the.following.factors.contribute.to.your.decision.in.choosing.Scripps.Research.for.graduate.school...External.factors.such.as.spouse.or.family.considerations.[106] <- "Modestly contributed"
inf_Enroll$How.did.the.following.factors.contribute.to.your.decision.in.choosing.Scripps.Research.for.graduate.school...Faculty.and.their.research.[21] <- "Modestly contributed"
inf_Enroll$How.did.the.following.factors.contribute.to.your.decision.in.choosing.Scripps.Research.for.graduate.school...Flexibility.of.program.[77] <- "Modestly contributed"
inf_Enroll$How.did.the.following.factors.contribute.to.your.decision.in.choosing.Scripps.Research.for.graduate.school...Location.[7] <- "Slightly contributed"
inf_Enroll$How.did.the.following.factors.contribute.to.your.decision.in.choosing.Scripps.Research.for.graduate.school...Stipend.and.benefits.[36] <- "Slightly contributed"
inf_Enroll$How.did.the.following.factors.contribute.to.your.decision.in.choosing.Scripps.Research.for.graduate.school...Stipend.and.benefits.[55] <- "Modestly contributed"
inf_Enroll$How.did.the.following.factors.contribute.to.your.decision.in.choosing.Scripps.Research.for.graduate.school...Stipend.and.benefits.[60] <- "Did not contribute"

inf_Enroll_melt <- melt(inf_Enroll, id = c("df_roger$What.year.are.you."))    # melt df
inf_Enroll_melt$variable2 <- gsub("[.]", " ", inf_Enroll_melt$variable)       # replace all "." with " "
inf_Enroll_melt$variable2 <- gsub("How did the following factors contribute to your decision in choosing Scripps Research for graduate school", " ", inf_Enroll_melt$variable2) # replace that phrase with nothing
inf_Enroll_melt$value <- factor(inf_Enroll_melt$value, levels = c("Strongly contributed",
                                                                  "Modestly contributed",
                                                                  "Slightly contributed",
                                                                  "Did not contribute"))     # Orders the Factor
```

## How factors contributed to decsion in choosing Scripps:

```{r, echo=FALSE}
ggplot(data = inf_Enroll_melt, aes(x = variable2, fill = value)) +
  geom_bar(color = "black", position = position_dodge(-.9)) +
  geom_text(stat = "count", aes(label = ..count..), position = position_dodge(-1), vjust = 0.4, hjust = -.25, size = 2.5) +
  labs(title = "How these factors contribute to your decision in choosing Scripps:", x = "", y = "") +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 20, simplify = FALSE), paste, collapse="\n")) + # Method of "wrapping x-axis text"
  scale_y_continuous(expand = c(0,0), limits = c(0,120), breaks = seq(0,120,20)) +
  scale_fill_brewer(name = "", palette ="Greys", labels = c("Strongly", "Modestly","Slightly","Did not")) +
  eval(parse(text = as.character(a_theme))) +
  theme(legend.position = c(0.9,0.9),
        axis.text.y = element_text(color = "black", size = 8, vjust = .5, face = "plain")) + 
  coord_flip()
```

## Graduate Schools Applied to and Accepted into. Some person got accepted to Zero Schools

```{r, echo=FALSE}
apply_accept <- cbind(df_roger$What.year.are.you., df_roger[29:30])
colnames(apply_accept) <- c("Year", "Applied", "Accepted")
apply_accept$id <- seq(1,length(apply_accept$Year))
aa_melt <- melt(apply_accept, id = c("id","Year"))

aa <- ggplot(data = aa_melt) +
  geom_boxplot(aes(x = variable, y = value)) +
  geom_point(aes(x = variable, y = value),alpha = 0.15, size = 1, shape = 21) +
  geom_line(aes(x = variable,y = value, group = id), alpha = 0.15) +
  labs(title = "Schools Applied and Accepted to", x = "", y = "") +
  scale_y_continuous(expand = c(0,0),limits = c(0,20), breaks = seq(0,20,2)) +
  eval(parse(text = as.character(a_theme))) +
  theme(legend.position = c(0.9,0.9),
        axis.text.y = element_text(color = "black", size = 8, vjust = .5, face = "plain"))

aa
```

### Faceted by Year

```{r}
aa + facet_grid(. ~ Year) + labs(title = "Schools Applied and Accepted to (by Year)")
```

## Before enrolling into grad school, I had the ... required to succeed (faceted by Year)

```{r, echo=FALSE}
begs <- cbind(df_roger$What.year.are.you., df_roger[31:35])
colnames(begs) <- c("Year", "Analytical & Research skills", "Writing & Communication skills", "Confidence & Motivation skills", "Knowledge of How Academia Works", "Support & Resources")

begs_melt <- melt(begs, id = c("Year"))
begs_melt$value <- factor(begs_melt$value, levels = c("Strongly disagree","Disagree","Neither agree nor disagree", "Agree","Strongly Agree" ))

ggplot(data = begs_melt) +
  geom_bar(aes(x = value)) +
  facet_grid(Year ~ variable)
```

```{r, echo=FALSE}
for (i in levels(begs_melt$variable)){
  plot <- ggplot(data = subset(begs_melt, begs_melt$variable == i)) +
    geom_bar(aes(x = value)) +
    geom_text(stat = "count", aes(label = ..count.., x = value), vjust = -.5) +
    labs(title = paste("Before grad school, I had the", i,"required to succeed", sep = " "), y = "", x = "") +
    scale_y_continuous(expand = c(0,0),limits = c(0,70), breaks = seq(0,70,10))+
    eval(parse(text = as.character(a_theme))) +
    theme(legend.position = c(0.9,0.9),
          axis.text.y = element_text(color = "black", size = 8, vjust = .5, face = "plain"),
          axis.title = element_text(color = "black", size = 5))
  print(plot)
}
```

## Grad Student Retreat

```{r, echo=FALSE}
retreat <- cbind(df_roger$What.year.are.you., df_roger[36:41])
retreat <- cbind(retreat, df_roger[43])
colnames(retreat) <- c("Year",
                       "GSS is an integral part to the Grad School Experience",
                       "I would still attend the GSS if it were Dry",
                       "My advisor has been supportive of me going to the GSS when it's off-campus",
                       "My advisor likely would be supportive of me going to the GSS when it's on-campus",
                       "I would attend the GSS if it were on campus",
                       "I am given enough opportunities to present to my research to my peers",
                       "The Distinguished lecture series is an integral part to the Grad School Experience")
retreat_melt <- melt(retreat, id = c("Year"))
retreat_melt$value <- factor(retreat_melt$value, levels = c("Strongly disagree","Disagree","Neither agree nor disagree", "Agree","Strongly agree" ))
```

```{r, echo=FALSE}
for (i in levels(retreat_melt$variable)){
  plot <- ggplot(data = subset(retreat_melt, retreat_melt$variable == i)) +
    geom_bar(aes(x = value)) +
    geom_text(stat = "count", aes(label = ..count.., x = value), vjust = -.5) +
    labs(title = i, y = "", x = "") +
    scale_y_continuous(expand = c(0,0),limits = c(0,70), breaks = seq(0,70,10))+
    eval(parse(text = as.character(a_theme))) +
    theme(legend.position = c(0.9,0.9),
          axis.text.y = element_text(color = "black", size = 8, vjust = .5, face = "plain"),
          axis.title = element_text(color = "black", size = 5))
  print(plot)
  print(plot+
          facet_grid(.~Year)+
          labs(title=paste(i, "\n By Year", sep="")))
}
```

## In your opinion, What is the most valuable part of the Graduate Student Symposium (GSS)?

```{r, echo=FALSE}
val_GSS <- cbind(df_roger[2], df_roger[42])
colnames(val_GSS) <- c("Year", "The most valuable part of GSS")
val_GSS <- melt(val_GSS, id = c("Year"))
val_GSS$value[31] <- "Bicoastal interactions" #Changed from "Its the only way to pay lipservice to Bicoastal Interactions"

ggplot(data = val_GSS) +
  geom_bar(aes(x = reorder(value, value, function(x)+length(x)))) +
  geom_text(stat = "count", aes(label = ..count.. , x = value), hjust = -0.25) + #adds count to each bar
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 15, simplify = FALSE), paste, collapse="\n")) + #method to wrap axis words
  scale_y_continuous(expand = c(0,0),limits = c(0,70), breaks = seq(0,70,10)) +
  labs(title = "What is the most valuable part of the GSS?", x = "", y = "") +
  coord_flip() +
  eval(parse(text = as.character(a_theme))) +
  theme(legend.position = c(0.9,0.9),
        axis.text.y = element_text(color = "black", size = 8, vjust = .5, face = "plain"),
        axis.title = element_text(color = "black", size = 5))
```

## Satisfaction with...

```{r, echo=FALSE}
satisfact <- cbind(df_roger[2], df_roger[44:53])
colnames(satisfact) <- c("Year",
                         "Selection of Professors in Graduate Program",
                         "Options for lab rotations",
                         "Choosing a lab to rotate in",
                         "Rotation Start & End",
                         "Team Teaching",
                         "Bicoastal Teaching",
                         "Number of Classes",
                         "Diversity of Classes",
                         "Amount of Course work",
                         "Course Rigor")
satisfact <- melt(satisfact, id = c("Year"))
satisfact$value <- factor(satisfact$value, levels = c("Very dissatisfied","Dissatisfied","Neutral", "Satisfied","Very satisfied"))
```

```{r, echo=FALSE}
for (i in levels(satisfact$variable)){
  plot <- ggplot(data = subset(satisfact, satisfact$variable == i)) +
    geom_bar(aes(x = value)) +
    geom_text(stat = "count", aes(label = ..count.., x = value), vjust = .9, color = "white") +
    labs(title = i, y = "", x = "") +
    scale_y_continuous(expand = c(0,0),limits = c(0,70), breaks = seq(0,70,10))+
    eval(parse(text = as.character(a_theme))) +
    theme(legend.position = c(0.9,0.9),
          axis.text.y = element_text(color = "black", size = 8, vjust = .5, face = "plain"),
          axis.title = element_text(color = "black", size = 5))
  print(plot)
  print(plot+
          facet_grid(.~Year)+
          labs(title = paste(i, "By Year", sep = " ")))
}
```

## Why did your education not meet your expectations? (Word Cloud)

```{r, echo=FALSE}
df_roger$If.your.educational.experiences.did.not.meet.your.expectations..why.. <- sub("^$", "No Response", df_roger$If.your.educational.experiences.did.not.meet.your.expectations..why..)
docs <- VCorpus(VectorSource(df_roger$If.your.educational.experiences.did.not.meet.your.expectations..why..))

```

Text cleaning
```{r, echo=FALSE}
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, removeWords, c("no response", "response", "no","can","etc", "take", "reason","use", "maybe", "like", "seen","quite","used","separate","student","butler","usually","spot","away","long"))
docs <- tm_map(docs, stripWhitespace)
docs <- tm_map(docs, removePunctuation)
docsCopy <- docs
docs <- tm_map(docs, stemDocument)
```
Transformation of data to a matrix then to dataframe. Create a vector (docs2) and complete the stemmed words.
```{r, echo=FALSE}
dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m), decreasing = TRUE)
d <- data.frame(word = names(v), freq = v)

docs2 <- stemCompletion(d$word, dictionary = docsCopy, type = "shortest")
```
Build Word Cloud with stemmed words as input word, and frequency.
```{r, echo=FALSE}
set.seed(1234)
wordcloud(words = docs2, freq = d$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```

## Recommend improvements to 1st and 2nd Year satisfaction? (Word Cloud) 

```{r, echo=FALSE}
df_roger$Can.you.recommend.any.improvements.towards.first.and.second.year.satisfaction. <- sub("^$", "No Response", df_roger$Can.you.recommend.any.improvements.towards.first.and.second.year.satisfaction.)
docs <- VCorpus(VectorSource(df_roger$Can.you.recommend.any.improvements.towards.first.and.second.year.satisfaction.))

```

Text cleaning
```{r, echo=FALSE}
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, removeWords, c("no response", "response", "no","can","etc", "take", "reason","use", "maybe", "like", "seen","quite","used","separate","student","butler","usually","spot","away","long"))
docs <- tm_map(docs, stripWhitespace)
docs <- tm_map(docs, removePunctuation)
docsCopy <- docs
docs <- tm_map(docs, stemDocument)
```
Transformation of data to a matrix then to dataframe. Create a vector (docs2) and complete the stemmed words.
```{r, echo=FALSE}
dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m), decreasing = TRUE)
d <- data.frame(word = names(v), freq = v)

docs2 <- stemCompletion(d$word, dictionary = docsCopy, type = "shortest")
```
Build Word Cloud with stemmed words as input word, and frequency.
```{r, echo=FALSE}
set.seed(1234)
wordcloud(words = docs2, freq = d$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```

## Satisfaction on other aspects of Scripps.
How satisfied are you with...

```{r, echo=FALSE}
satisfact2 <- cbind(df_roger$What.year.are.you.,df_roger[56:62])
colnames(satisfact2) <- c("Year",
                          "The graduate program overall",
                          "Your educational experience",
                          "The Graduate office staff",
                          "The Teaching Faculty",
                          "TSRI Executive Office",
                          "Core Facilities",
                          "Library Resources")
satisfact2 <- melt(satisfact2, id = c("Year"))
satisfact2 <- satisfact2[-c(74,188,302,416,530,644,758),]   # remove empty row (one persone skilled this.)
satisfact2$value <- factor(satisfact2$value, levels = c("Very Dissatisfied","Dissatisfied","Neutral", "Satisfied","Very satisfied"))
```

```{r, echo = FALSE}
for (i in levels(satisfact2$variable)){
  plot <- ggplot(data = subset(satisfact2, satisfact2$variable == i)) +
    geom_bar(aes(x = value)) +
    geom_text(stat = "count", aes(label = ..count.., x = value), vjust = .9, color = "white") +
    labs(title = paste("How satisfied are you with",i, sep = " "), y = "", x = "") +
    scale_y_continuous(expand = c(0,0),limits = c(0,80), breaks = seq(0,80,10))+
    eval(parse(text = as.character(a_theme))) +
    theme(legend.position = c(0.9,0.9),
          axis.text.y = element_text(color = "black", size = 8, vjust = .5, face = "plain"),
          axis.title = element_text(color = "black", size = 5))
  print(plot)
  #print(plot+facet_grid(.~Year))
}
```

## Recommendations for co-mentorship (Word Cloud)

```{r, echo=FALSE}
df_roger$Is.there.anything.else.you.would.like.to.share.regarding.co.advising. <- sub("^$", "No Response", df_roger$Is.there.anything.else.you.would.like.to.share.regarding.co.advising.)
docs <- VCorpus(VectorSource(df_roger$Is.there.anything.else.you.would.like.to.share.regarding.co.advising.))

```

Text cleaning
```{r, echo=FALSE}
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, removeWords, c("no response", "response", "no","can","etc", "take", "reason","use", "maybe", "like", "seen","quite","used","separate","student","butler","usually","spot","away","long"))
docs <- tm_map(docs, stripWhitespace)
docs <- tm_map(docs, removePunctuation)
docsCopy <- docs
docs <- tm_map(docs, stemDocument)
```
Transformation of data to a matrix then to dataframe. Create a vector (docs2) and complete the stemmed words.
```{r, echo=FALSE}
dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m), decreasing = TRUE)
d <- data.frame(word = names(v), freq = v)

docs2 <- stemCompletion(d$word, dictionary = docsCopy, type = "shortest")
```
Build Word Cloud with stemmed words as input word, and frequency.
```{r, echo=FALSE}
set.seed(1234)
wordcloud(words = docs2, freq = d$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```
